Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Clarify paragraph on near-wake stuff

Previously, is has been observed experimentally that a high solidity cross-flow
turbine wake's unique vortical mean flow field is responsible for accelerated
wake recovery when compared with conventional axial-flow propeller-type turbines
\cite{Bachant2015-JoT}. In this study we seek to replicate the same momentum and
energy balance considerations at multiple Reynolds numbers, to examine the
implications on how small scale, i.e. low Reynolds number experiments may be
used to study flows in turbine arrays.

>>>>

Vertical-axis wind turbine array field experiments have revealed that
accelerated wake recovery allows for closer spacing when compared with
conventional axial-flow propeller-type turbines \cite{Dabiri2011, Kinzel2012}.
It was observed experimentally that a high solidity vertical-axis cross-flow
turbine's near-wake produces a unique vertical mean velocity field---generated
by blade tip vortex shedding---the advection by which is the largest contributor
to streamwise momentum and energy transport or recovery \cite{Bachant2015-JoT}.
In this study we seek to replicate those same momentum and energy balance
considerations at multiple Reynolds numbers, to examine the implications on how
small scale, i.e. low Reynolds number experiments may be used to study flows in
turbine arrays.
